Mixed Non-Bayesian and DeGroot Learning

### 2012-12-09 docs/paper.tex
Brief section on network structure

(Mixed Non-Bayesian and DeGroot nodes)

>>>>

The network in our model consists of an undirected graph where each vertex is either a Non-Bayesian or a DeGroot node.  At each discrete timestep $t$, every node will perform a belief update of its corresponding type.  If two vertices are connected by an edge, they are said to be neighbors and will incorporate each others' beliefs in their respective updates.

The model allows for a variety of generative methods to be used for creation of the network structure such as Erdos-Renyi, Watts-Strogatz, Kleinberg's Small-World Model, or a power law distribution.  We investigate each of these network types in section \{ \}.% @todo[DDC] Refer to simulation results
